Extending statistical models for source attribution of zoonotic diseases: A study of campylobacteriosis

### 2018-03-22 paper/finalish/article.tex
update tables.r to compute DICs for each model, and update the corresponding table in the text

\begin{table}
  \begin{center}
    \begin{tabular}{crrrrr}
      \toprule
      & \multicolumn{2}{c}{Island model}  & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Dirichlet model} \\
      Data & Linear & Categorical & & Linear & Categorical\\ \midrule
      whole period  & 7913.6 & 7943.3  & & 10328.4  & 10389.8 \\
      post-intervention period  & 5413.4  & 5439.5  & & 6615.1   & 6668.9 \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{DIC values for the linear model and for the categorical model applied to the data from 2005 to 2014 (whole period) and to the data from 2008 to 2014 (post-intervention period) given the genotypic information is from the asymmetric Island model or the Dirichlet model.}
  \label{tab:dic}
\end{table}

>>>>

\begin{table}
  \begin{center}
	\begin{tabular}{lrr}
	\toprule
	Model & Dirichlet & Island\\
	\midrule
	Linear & 10,968.3 & 12,276.4\\
	Categorical & 10,976.4 & 12,287.2\\
	\bottomrule
	\end{tabular}
  \end{center}
  \caption{DIC values for the linear model and for the categorical model applied to the data from 2005 to 2014 for the the asymmetric Island and Dirichlet models.}
  \label{tab:dic}
\end{table}
